\documentclass[10pt]{report}

\usepackage{enumerate} % for enumerate counter
\usepackage{subcaption} % for subfigures
\usepackage{amsthm} % for QED
\usepackage{mathtools} % for delimiter

\usepackage{listings} % for code
\lstset{ 
	language=R,
	basicstyle=\footnotesize\ttfamily,
	numbers=none,
	stepnumber=1,
	numbersep=8pt,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	frame=single,
	tabsize=2,
	captionpos=t,
	breaklines=true,
	breakatwhitespace=false
} 

\usepackage{float} % for figure [H]
\usepackage{booktabs} % for tabular
\usepackage{caption} % for \caption*
\usepackage[export]{adjustbox} % for valign=t
\usepackage{array} % for column type m
\usepackage{verbatim}
\usepackage{graphicx}
%\graphicspath{ {imgs/} }
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsmath}

%%%%%%Pagination
\setlength{\topmargin}{-.3 in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textheight}{9.in}
\setlength{\textwidth}{6.5in}

%Cover
\newcommand{\hwTitle}{Homework \#6}
\newcommand{\hwCourse}{Applied Statistics}
\newcommand{\hmClassInstructor}{Professor Lulu Kang}

\title{
	\vspace{2in}
	\textmd{\textbf{\hwCourse\\\hwTitle}}\\
	\vspace{0.3in}\large{\textit{\hmClassInstructor}}
	\vspace{3in}
}
\author{\textbf{Zhihao Ai}}
\date{}

%Header
\pagestyle{fancy}
\fancyhead[L]{Zhihao Ai}
\fancyhead[C]{Math 484}
\fancyhead[R]{Homework 6}
%%%%%%

%Global settings
%\everymath{\displaystyle}
\setlength\parindent{0pt}

%Custom commands
\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}

\newcolumntype{N}{>$ c <$}
\newcolumntype{M}[1]{>{\centering\arraybackslash $}m{#1}<{$}}

\newcommand{\abs}[1] {\left| #1 \right|}

\DeclarePairedDelimiter\autoparen{(}{)}
\newcommand{\pa}[1]{\autoparen*{#1}}

\newcommand{\var} {\text{var}}

\newcommand{\m}[1] {\mathbf{#1}}

\begin{document}

\maketitle

\section*{Problem 1}
(Ex. 14.9) \textbf{Performance ability} + (Ex. 14.10(a))
\begin{enumerate}[a.]
	\item 
	Find the maximum likelihood estimate of $\beta_0$ and $\beta_1$. State the fitted response function.
	
	\item 
	Obtain a scatter plot of the data with both the fitted logistic response function from part (a) and a lowess smooth superimposed. Does the fitted logistic response function appear to fit well?
	
	\item 
	Obtain $\exp{b_1}$ and interpret this number.
	
	\item 
	What is the estimated probability that employees with an emotional stability test score of 550 will be able to perform in a task group?
	
	\item 
	Estimate the emotional stability test score for which 70 percent of the employees with this test score are expected to be able to perform in a task group.
	
	\item 
	Fit a probit mean response function (14.12) to the data. Quantitatively compare the fit here with the logistic fit obtain in part (a). What do you conclude?
\end{enumerate}

\section*{Problem 2}
(Ex. 14.13) \textbf{Car purchase}
\begin{enumerate}[a.]
	\item 
	Find the maximum likelihood estimates of $\beta_0$, $\beta_1$ and $\beta_2$. State the fitted response function.
	
	\item 
	Obtain $\exp{b_1}$ and $\exp{b_2}$ and interpret these numbers.
	
	\item 
	What is the estimated probability that a family with annual income of \$50 thousand and an oldest car of 3 years will purchase a new car next year?
\end{enumerate}

\section*{Problem 3}
(Ex. 14.12) \textbf{Toxicity experiment}
\begin{enumerate}[a.]
	\item 
	Plot the estimated proportions $p_j = Y_j / n_j$ against $X_j$. Does the plot support the analyst's belief that the logistic response function is appropriate?
	
	\item 
	Find the maximum likelihood estimates of $\beta_0$ and $\beta_1$. State the fitted response function.
	
	\item 
	Obtain a scatter plot of the data with the estimated proportions from part (a), and superimpose the fitted logistic response function from part (b). Does the fitted logistic response function appear to fit well?
	
	\item 
	Obtain $\exp{b_1}$ and interpret this number.
	
	\item 
	What is the estimated probability that an insect dies when the dose level is $X=3.5$?
	
	\item 
	What is the estimated median lethal dose---that is, the dose for which 50 percent of the experimental insects are expected to die?
\end{enumerate}

\end{document}

